Public Health Intervention Visualisation

### 2020-09-09 FEM_R/ELSA_data_check.Rmd
Added lots of R scripts for visualising and checking data

# Diabetes
diabe <- H_ELSA_base %>% select(matches('r[0-9]diabe$'))
apply(diabe, 2, pMiss)

>>>>

# Diabetes
diabe <- H_ELSA_base %>% select(matches('r[0-9]diabe$'))
apply(diabe, 2, pMiss)
print(' ')

# Lung Disease
lunge <- H_ELSA_base %>% select(matches('r[0-9]lunge$'))
apply(lunge, 2, pMiss)
print(' ')

# smoken and smokev and smokef
smoken <- H_ELSA_base %>% select(matches('r[0-9]smoken$'))
apply(smoken, 2, pMiss)
print(' ')
smokev <- H_ELSA_base %>% select(matches('r[0-9]smokev$'))
apply(smokev, 2, pMiss)
print(' ')
smokef <- H_ELSA_base %>% select(matches('r[0-9]smokef$'))
apply(smokef, 2, pMiss)
print(' ')

# drink
drink <- H_ELSA_base %>% select(matches('r[0-9]drink$'))
apply(drink, 2, pMiss)
print(' ')

### 2020-09-09 FEM_R/pubHealthInterventionVis_Notebook.Rmd
Added lots of R scripts for visualising and checking data

# Smoking variables and chronic diseases
ggplot(cohort, aes(x=age, y=n_smoke_stop_all)) +
        geom_line(col='black', size=0.3) +
        geom_line(data=x169, size=0.3, col='red') +
        labs(title='Smoke Stop', y='# Stopped Smoking', x='Age')
ggplot(cohort, aes(x=age, y=p_smoken_all)) +
        geom_line(col='black', size=0.3) +
        geom_line(data=x169, size=0.3, col='red') +
        labs(title='Prevalence of Smoking by Age', y='Prevalence of Smoking', x='Age')
ggplot(cohort, aes(x=age, y=p_lunge_all)) +
        geom_line(col='black', size=0.3) +
        geom_line(data=x169, size=0.3, col='red') +
        labs(title='Prevalence of Lung Disease by Age', y='Prevalence of Lung Disease', x='Age')
ggplot(cohort, aes(x=age, y=p_cancre_all)) +
        geom_line(col='black', size=0.3) +
        geom_line(data=x169, size=0.3, col='red') +
        labs(title='Prevalence of Cancer by Age', y='Prevalence of Cancer', x='Age')
```

>>>>

# Smoking variables and chronic diseases
ggplot(cohort, aes(x=age, y=n_smoke_stop_all)) +
        geom_line(col='black', size=0.3) +
        geom_line(data=x169, size=0.3, col='red') +
        labs(title='Smoke Stop', y='# Stopped Smoking', x='Age')
ggplot(cohort, aes(x=age, y=n_smoke_start_all)) +
        geom_line(col='black', size=0.3) +
        geom_line(data=x169, size=0.3, col='red') +
        labs(title='Smoke Start', y='# Started Smoking', x='Age')
ggplot(cohort, aes(x=age, y=p_smoken_all)) +
        geom_line(col='black', size=0.3) +
        geom_line(data=x169, size=0.3, col='red') +
        labs(title='Prevalence of Smoking by Age', y='Prevalence of Smoking', x='Age')
ggplot(cohort, aes(x=age, y=p_lunge_all)) +
        geom_line(col='black', size=0.3) +
        geom_line(data=x169, size=0.3, col='red') +
        labs(title='Prevalence of Lung Disease by Age', y='Prevalence of Lung Disease', x='Age')
ggplot(cohort, aes(x=age, y=p_cancre_all)) +
        geom_line(col='black', size=0.3) +
        geom_line(data=x169, size=0.3, col='red') +
        labs(title='Prevalence of Cancer by Age', y='Prevalence of Cancer', x='Age')
```
